\begin{thebibliography}{99}

\bibitem{Pomerance}
Pomerance, Carl. A Tale of Two Sieves

\bibitem{Pollard}
J. M. Pollard (1988). Factoring with cubic numbers

\bibitem{Pomerance}
И. В. Агафонова. Факторизация больших целых чисел и криптография.

\bibitem{Briggs}
Briggs M. (1998). An Introduction to the General Number Field Sieve

\bibitem{Pomerance}
Ишмухаметов Ш. Т. Методы факторизации натуральных чисел. \\ — Казань: Казан. ун.. — 2011. — 190 с.

\bibitem{Cavallar}
Cavallar S., Dodson B., Lenstra A. K., Leyland P. C., Lioen W. M., Montgomery P. L., Murphy B., te Riele H. J. J., Zimmerman P. Factorization of RSA-140 using the number field sieve / CWI Report MAS-R9925, September 1999.

\bibitem{Kormen}
Michael Case. Oregon State University, ECE 575. A Beginner’s Guide To The General Number Field Sieve 

https://citeseerx.ist.psu.edu/viewdoc/download?doi=10.1.1.219.2389\&\\rep=rep1\&type=pdf

\bibitem{Kormen}
Detailed Example: Quadratic Sieve Factorization

https://www.youtube.com/watch?v=5ekTew5Kj7w\&list\\=PLKXdxQAT3tCssgaWOy5vKXAR4WTPpRVYK\&index=30


\bibitem{Kormen}
Dixon's factorization method
https://en.wikipedia.org/wiki/Dixon\%27s\_factorization\\\_method\#:~:text=In\%20number\%20theory\%2C\%20Dixon's\%20factorization,the\%20\\prototypical\%20factor\%20base\%20method.\&text=The\%20algorithm\%20was\\\%20designed\%20by,and\%20was\%20published\%20in\%201981

\bibitem{Kormen}
The Quadratic Sieve Factoring Algorithm
Eric Landquist
MATH 488: Cryptographic Algorithms
December 14, 2001
http://www.cs.virginia.edu/crab/QFS\_Simple.pdf

\end{thebibliography}